Regularising Lotka--Volterra Interaction Matrices by Species Grouping

### 2021-10-07 article.rnw
Add a local bibliography file.
Add the forest package, and define a style for phylogenetic trees.
Add the phylogeny of the study species to the methods.

%Referencing
\import{reference-styles/}{authoryear.tex}
\addbibresource{bibliography/references.bib}
\usepackage{placeins} %Provides \FloatBarrier

\usepackage{hyperref}

@@

>>>>

%Images
\usepackage{tikz}
\usepackage[edges]{forest}

%Referencing
\import{reference-styles/}{authoryear.tex}
\addbibresource{bibliography/references.bib}
\addbibresource{references.bib}
\usepackage{placeins} %Provides \FloatBarrier

\usepackage{hyperref}
\usepackage{cleveref}

\forestset{
	phylogeny/.style={
		forked edges,
		delay={where content={}{shape=coordinate}{}}, %Make empty nodes leave no gaps.
		before typesetting nodes={
			where n children=0{tier=terminus}{},
		},
		for tree={
			grow=east,
			align=left,
			anchor=west,
			s sep=0, %Reduce the separation between the leaf nodes.
		}
	}
}

@@

\subsubsection{Phylogeny}

I determined the phylogenic relationships between the six study species, by examination of the literature, in order to compare these to the groupings generated by the models.
No attempt was made to determine absolute phylogenetic distances, for sufficient data was not available on all six species for this purpose.
Rather, I only determined relative times of evolutionary divergence sufficient to form a binary phylogenetic tree.

\Textcite{terry2021natural} give the subgroups of the genus to which each study species belongs.
\Textcite{lewis2005phylogeny} gives the relationship between three of these subgroups (melanogaster, ananassae, and montium), all of the subgenus Sophophora, while \textcite{izumitani2016phylogeography} describe the fourth subgroup (nasuta) as belonging to the distinct Drosophila subgenus.
From this can be constructed the necessary relationships, which are depicted in \cref{fig:phylogeny}.

\begin{figure}
	\centering
	\begin{forest} phylogeny
		[
			[
				[
					[\emph{D. melanogaster}]
					[\emph{D. birchii}]
				]
				[
					[\emph{D. pandora}]
					[\emph{D. pseudoananassae}]
				]
			]
			[
				[
					[\emph{D. pallidifrons}]
					[\emph{D. sulfurigaster}]
				]
			]
		]
	\end{forest}

	\caption{%
		The phylogenetic relationships between the six \emph{Drosophila} species in the study.
		The relationships depicted are purely qualitative; no implication of phylogenetic distance is made.
	}
	\label{fig:phylogeny}
\end{figure}
